---
title: "truenumbers"
author: "Hao He"
date: "2022-10-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sentimentr)
```

```{r echo = FALSE}
library(tnum)
tnum.loadLibs()
tnum.authorize(ip="mssp.truenum.com:8080",creds = "haohe@bu.edu:marmoset")

```
# Book report without reading
The strategy is to track the action and ideas in the book so you can used this maerial as raw material for a report.  You might conclude you report by posing the questions that the book poses. 
```{r}
# stringval
tnum.query("stringval:The Time Traveller and stringval:Morlock") #1
tnum.query("stringval:The Time Traveller") #57
tnum.query("stringval:me and stringval: Weena") #27 results
tnum.query("stringval:time travel and stringval:")

# try chapters

text_ch1 <- tnum.query("subj:Time_Machine:Chapter:1:*")
text_ch2 <- tnum.query("subj:Time_Machine:Chapter:2:*")
text_ch4 <- tnum.query("subj:Time_Machine:Chapter:4:*")
text_ch5 <- tnum.query("subj:Time_Machine:Chapter:5:*")
text_ch6 <- tnum.query("subj:Time_Machine:Chapter:6:*")
text_ch7 <- tnum.query("subj:Time_Machine:Chapter:7:*")
text_ch8 <- tnum.query("subj:Time_Machine:Chapter:8:*")
text_ch10 <- tnum.query("subj:Time_Machine:Chapter:10:*")
text_ch12 <- tnum.query("subj:Time_Machine:Chapter:12:*")

ch8_weena <- tnum.query("subj:Time_Machine:Chapter:8:* and stringval:Weena")
ch10_weena <- tnum.query("subj:Time_Machine:Chapter:10:* and stringval:Weena")
ch11_weena <- tnum.query("subj:Time_Machine:Chapter:11:* and stringval:Weena")
ch12_weena <- tnum.query("subj:Time_Machine:Chapter:12:* and stringval:Weena")
ch13_weena <- tnum.query("subj:Time_Machine:Chapter:13:* and stringval:Weena")
all_weena <- tnum.query("subj:Time_Machine:* and stringval:Weena") #53 
kable(all_weena)

tnum.query("subj:Time_Machine:Chapter:13:*")




###############Tina's work

time_weena <- tnum.query("stringval:weena")%>%
  select(subject, value) %>%
  separate(subject, sep=":",
    into=c("book","chap","chap_no", "sent","sent_no")) %>%
  select(chap_no, sent_no, value)
   time_weena$chap_no <- as.numeric(time_weena$chap_no)
   time_weena$sent_no <- as.numeric(time_weena$sent_no)
time_weena %>% arrange(chap_no, sent_no)
w <- tnum.query("stringval:weena*")

time_wee_mor <- tnum.query("stringval:weena and stringval:morlock") %>%
               select(subject, value) %>%
               separate(subject, sep=":",
      into=c("book","chap","chap_no", "sent","sent_no")) %>%
               select(chap_no, sent_no, value)
time_wee_mor$chap_no <- as.numeric(time_wee_mor$chap_no)
time_wee_mor$sent_no <- as.numeric(time_wee_mor$sent_no)
time_wee_mor %>% arrange(chap_no, sent_no) 



# where me , weena, morlock mentioned
me_weena_morlock<- tnum.query("stringval:weena and stringval:morlock and stringval:me") %>%
               select(subject, value) %>%
               separate(subject, sep=":",
      into=c("book","chap","chap_no", "sent","sent_no")) %>%
               select(chap_no, sent_no, value)
me_weena_morlock$chap_no <- as.numeric(time_wee_mor$chap_no)
me_weena_morlock$sent_no <- as.numeric(time_wee_mor$sent_no)
table_me_weena_morlock<- me_weena_morlock%>% arrange(chap_no, sent_no) 

# 
weena_machine<- tnum.query("stringval:weena and stringval:time machine") %>%
               select(subject, value) %>%
               separate(subject, sep=":",
      into=c("book","chap","chap_no", "sent","sent_no")) %>%
               select(chap_no, sent_no, value)

view(weena_machine)


# morlock mentioned
time_morlock <- tnum.query("stringval:morlock") %>%
                select(subject, value) %>%
                separate(subject, sep=":",
    into=c("book","chap","chap_no", "sent","sent_no")) %>%
     select(chap_no, sent_no, value)
time_morlock$chap_no <- as.numeric(time_morlock$chap_no)
time_morlock$sent_no <- as.numeric(time_morlock$sent_no)
time_morlock %>% arrange(chap_no, sent_no)
view(time_morlock %>% arrange(chap_no, sent_no))


# narrator/Hillyer

# sentiment analysis by chapters
library(sentimentr)
time_m_ch_8 <- tnum.query("Time_Machine:chapter:8:sentence:* has text") %>%
  select(subject, value) %>%
  separate(subject, sep=":",
           into=c("book","chap","chap_no", "sent","chap8_sent_no")) %>%
  select(chap8_sent_no, value)

time_m_ch_8$chap8_sent_no <- as.numeric(time_m_ch_8$chap8_sent_no)
time_m_ch_8 %>% arrange(chap8_sent_no)
time_m_ch_8_pick_section <- time_m_ch_8 %>%
  filter(90 < chap8_sent_no & chap8_sent_no < 130) %>%
  select(value)
time_m_ch_8_pick_section_sent <- time_m_ch_8_pick_section %>%
  get_sentences() %>%
  sentiment()
time_m_ch_8_pick_section_sent %>%
  ggplot() + geom_density(aes(sentiment))

# 
time_m_ch_12 <- tnum.query("Time_Machine:chapter:12:sentence:* has text") %>%
  select(subject, value) %>%
  separate(subject, sep=":",
           into=c("book","chap","chap_no", "sent","chap12_sent_no")) %>%
  select(chap12_sent_no, value)

time_m_ch_2$chap12_sent_no <- as.numeric(time_m_ch_8$chap8_sent_no)
time_m_ch_8 %>% arrange(chap8_sent_no)
time_m_ch_8_pick_section <- time_m_ch_8 %>%
  filter(90 < chap8_sent_no & chap8_sent_no < 130) %>%
  select(value)
time_m_ch_8_pick_section_sent <- time_m_ch_8_pick_section %>%
  get_sentences() %>%
  sentiment()
time_m_ch_8_pick_section_sent %>%
  ggplot() + geom_density(aes(sentiment))
```

# Demographics of New England counties
Education, wealth, poverty, or correlations between variables in the dataset. 
Discuss how you approached the data, what you found, what you wonder about what you found, and so on.
```{r}
# example
x_nhi_mas <- tnum.query("subj:Massachusetts* and prop:population:no_health_insurance and numval:>20000")
xmas <-  mapply(FUN = tnum.addTag,
       guid = x_nhi_mas$id,
       tag = "pop no_health_insurance",
       text = "the population of no helath insurance in Massachusetts")
tnum.getTagsOfTn(x_nhi_mas[1,]$id)
kable(x_nhi_mas)

tn1 <- tnum.postStatement(
  stmt = "The largest number of Massachusetts at Middlesex that not having health insurance is 39401 ",
  notes = "Our first truenumber"
)

# tnumgraphics




tnum.query("subj:Massachusetts* and prop:population")

tnum.getAllProperties()
tmp <- tnum.query("prop:population")
colnames(tmp)

```

```{r}
tnum.query("prop:population and ")

tnum.query("subj:")
```

